О множествах точек на плоскости с целочисленными расстояниями

### 2019-06-01 pps-linear-bound/pps-linear-lower-bound.tex
Translated version of the involved results

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{observation}[theorem]{Observation}

@@

Summing up Construction~\ref{con:planar_set_with_minimeter_1} above with~\cite[lemma 3 and proposition 6]{our-vmmsh-2018}
and~\cite[Section 6]{antonov2008maximal},
we obtain the following

TODO: write the translated version of the results here

>>>>

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{conjecture}[theorem]{Conjecture}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{observation}[theorem]{Observation}

@@

If the take $k=1$ in Lemma~\ref{lem:2k-1_segments},
we obtan the following result (which is exactly~\cite[Lemma 3]{our-vmmsh-2018}).
\begin{corollary}
	\label{cor:only_one_distance_1_on_straight_line}
	Let $M \in \mathfrak{M}(2,n)$ for some $n$ and let $m$ be a straight line.
	Then there is at most one pair of points $M_1,M_2\in M \cap m$
	such that $|M_1 M_2| = 1$.
\end{corollary}

To describe all the sets $M \in \mathfrak{M}(2,n)$ with distance 1,
we will need~\cite[Proposition 6]{our-vmmsh-2018}.
For the sake of completeness, we will give here a slightly rephrased version of it with the proof as
\begin{lemma}
	\label{lem:no_4_points_in_semigeneral_position_with_distance_1}
	Let $M=\{M_1,M_2,M_3,M_4\}\in \mathfrak{M}(2,4)$ such that $|M_1 M_2|=1$
	and let $l$ be the straight line containing points $M_1$ and $M_2$.
	Then one of the points $M_3$ or $M_4$ belongs to $l$.
\end{lemma}

\begin{proof}
	Let $m$ denote the bisector of line segment $M_1 M_2$.
	Due to the triangle inequality, there are two possibilities to place each of points $M_i$, $i=3,4$:

	a) $M_i$ belongs to $l$ and $|M_i M_1|-|M_i M_2| = \pm 1$;

	b) $M_i$ belongs to $m$ and $|M_i M_1| = |M_i M_2|$.

	If (a) is true for both points, then $M\subset l$ and thus $M$ is not an integral point set.
	If (a) is true for one point and (b) is true for another, then the claim of the lemma follows.
	So, suppose the contrary, i.e. both points $M_3$ and $M_4$ belong to $m$.

	The area of the triangle $M_1 M_3 M_4$ is rational because $|M_3 - M_4| \in \mathbb{Z}$.
	Thus, the set $M$ is of characteristic 1,
	and there is a Cartesian coordinate system such that $M_1=(-1/2,0)$, $M_2=(1/2,0)$, $M_3=(0, a/2)$.
	(TODO: ref?)
	It is clear that $a\neq 0$.
	We set $b = |M_1 - M_3|$ and $O=(0,0)$.
	Applying the Pythagorean theorem to triangle $OM_1M_3$, we obtain the following Diophantine equation:
	\begin{equation}
		\frac{1}{4} + \frac{a^2}{4} = b^2
		,
	\end{equation}
	or, which is the same,
	\begin{equation}
		1 + a^2 = (2b)^2
		,
	\end{equation}
	that has no integral solutions.
	This contradiction concludes the proof.
\end{proof}

Using Construction~\ref{con:planar_set_with_minimeter_1},
Lemma~\ref{lem:no_4_points_in_semigeneral_position_with_distance_1} and Corollary~\ref{cor:only_one_distance_1_on_straight_line}
together with results of~\cite[Section 6]{antonov2008maximal},
we obtain the following
